---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

palette(c("#0073C2", "#EFC000", "#868686"))
```

```{r, function_max_output_lines, include = FALSE}
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
``` 

# clubpro

<!-- badges: start -->
![](https://www.r-pkg.org/badges/version-ago/clubpro?color=orange)
![](https://cranlogs.r-pkg.org/badges/grand-total/clubpro) 
[![R-CMD-check](https://github.com/timbeechey/clubpro/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/timbeechey/clubpro/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/timbeechey/clubpro/branch/master/graph/badge.svg)](https://app.codecov.io/gh/timbeechey/clubpro?branch=master)
<!-- badges: end -->

An R package for *cl*assification *u*sing *b*inary *p*rocrustes *ro*tation based on Grice (2011).

## Installation

`clubpro` can be installed from CRAN:

```{r install_cran, eval=FALSE}
install.packages("clubpro")
```

Install the development version of `clubpro` from [GitHub](https://github.com/timbeechey/clubpro) with:

```{r install_github, eval=FALSE}
# install.packages("remotes")
remotes::install_github("timbeechey/clubpro")
```

## Background

`clubpro` is an implementation of a subset of the methods described in [Grice (2011)](https://psycnet.apa.org/record/2011-14580-000).

## Using `clubpro`

```{r load_clubpro}
library(clubpro)
library(carData)
```

For this example we'll use the `Friendly` dataset from the `carData` package.

```{r load_data}
data(Friendly, package = "carData")
dat <- Friendly
```

This data set consists of counts of correctly recalled words (out of 40) across three experimental conditions.

```{r inspect_data}
str(dat)
```

Run the model to quantify how well each count of `correct` recalled words is classified in terms of `condition`.

```{r run_model}
mod <- club(correct ~ condition, data = dat, nreps = 1000)
```

Print a summary of the model output.

```{r model_summary}
summary(mod)
```

Plot the classification results.

```{r plot}
plot(mod)
```

# References

Grice, J. W. (2011). _Observation oriented modeling: Analysis of cause in the behavioral sciences_. Academic Press.
