---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

```{r, function_max_output_lines, include = FALSE}
library(knitr)
hook_output <- knit_hooks$get("output")
knit_hooks$set(output = function(x, options) {
  lines <- options$output.lines
  if (is.null(lines)) {
    return(hook_output(x, options))  # pass to default hook
  }
  x <- unlist(strsplit(x, "\n"))
  more <- "..."
  if (length(lines)==1) {        # first n lines
    if (length(x) > lines) {
      # truncate the output, but add ....
      x <- c(head(x, lines), more)
    }
  } else {
    x <- c(more, x[lines], more)
  }
  # paste these lines together
  x <- paste(c(x, ""), collapse = "\n")
  hook_output(x, options)
})
``` 

# clubpro

An R package for *cl*assification *u*sing *b*inary *p*rocrustes *ro*tation based on Grice (2011).

## Installation

Install the development version of `clubpro` from [GitHub](https://github.com/timbeechey/clubpro) with:

```{r install_github, eval=FALSE}
# install.packages("remotes")
remotes::install_github("timbeechey/clubpro")
```

## Citation

To cite `clubpro` in your work you can use the output of:

```{r citation, eval=FALSE, message=FALSE, warning=FALSE}
citation(package = "clubpro")
```

## Background

`clubpro` is an implementation of methods described in [Grice (2011)](https://psycnet.apa.org/record/2011-14580-000).

## using `clubpro`

```{r load_clubpro}
library(clubpro)
library(lattice)
```

Simulate some count data.

```{r simulate_data}
set.seed(123)

n <- 300

dat <- data.frame(x = rep(c("A","B","C"), each = n),
                  y = c(rpois(n, lambda = 10),
                        rpois(n, lambda = 15),
                        rpois(n, lambda = 20)))

dat$x <- factor(dat$x)

histogram( ~ y | x, data = dat, layout = c(1,3))
```

Run the model.

```{r run_model}
mod <- with(dat, club(y, x))
```

Print a summary of the model output (note: only the first 50 lines of output are shown here).

```{r model_summary, output.lines = 50}
summary(mod)
```

Plot the classification results.

```{r plot}
plot(mod)
```

# References

Grice, J. W. (2011). _Observation oriented modeling: Analysis of cause in the behavioral sciences_. Academic Press.
