---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# clubpro

An R package for *cl*assification *u*sing *b*inary *p*rocrustes *ro*tation based on Grice (2011).

## Installation

Install the development version of `clubpro` from [GitHub](https://github.com/timbeechey/clubpro) with:

```{r install_github, eval=FALSE}
# install.packages("remotes")
remotes::install_github("timbeechey/clubpro")
```

## Citation

To cite `clubpro` in your work you can use the output of:

```{r citation, eval=FALSE, message=FALSE, warning=FALSE}
citation(package = "clubpro")
```

## Background

`clubpro` is an implementation of methods described in [Grice (2011)](https://psycnet.apa.org/record/2011-14580-000).

## using `clubpro`

```{r load_clubpro}
library(clubpro)
```



# References

Grice, J. W. (2011). _Observation oriented modeling: Analysis of cause in the behavioral sciences_. Academic Press.
